A primer to numerical simulations: The perihelion motion of Mercury

### 2018-04-17 tex/MercuryNumerical.tex
CH edits 2

The idea that the numerical study of the perihelion motion of Mercury is an interesting subject for high school students was taken from a project work of one of the authors (JH).
The project was eventually presented at the M\"adchen-Gymnasium J\"ulich (a German high school) in 11$^{\rm th}$ grade in 2014.
Based on this study, the course was developed as outlined in Sec.~\ref{sec:Numerical Implementation} and used in the Sch\"ulerakademie Teilchenphysik in 2015, which aims at high school students from 10$^{\rm th}$ to 13$^{\rm th}$ grade.
This academy is financed by the German Research Society (DFG) as the outreach branch of a research grant focussing on basic research in particle and nuclear physics.
One of the authors (CH) is acting as a Principal Investigator for the outreach activities within this scheme.
The Sch\"ulerakademie Teilchenphysik runs biannually at the Science Center Overbach in J\"ulich for four days and has about 25 participants coming from various parts of Germany.
The academy comprises lectures, a tour to the particle accelerator COSY as well as the high performance computing facility at the Research Center J\"ulich as well as one full day of practical work.
Given the setting the participating students are highly motivated and eager to understand.

>>>>

The idea that the numerical study of the perihelion motion of Mercury is an interesting subject for high school students was taken from a project work of one of the authors (JH).
The project was presented at the M\"adchen-Gymnasium J\"ulich (a German high school) in 11$^{\rm th}$ grade in 2014.
Based on this study, the course was developed as outlined in Sec.~\ref{sec:Numerical Implementation} and used in the Sch\"ulerakademie Teilchenphysik in 2015, which aims at high school students from 10$^{\rm th}$ to 13$^{\rm th}$ grade.
This academy is financed by the German Research Society (DFG) as the outreach branch of a research grant focussing on basic research in particle and nuclear physics.
One of the authors (CH) is acting as a Principal Investigator for the outreach activities within this scheme.
The Sch\"ulerakademie Teilchenphysik runs biannually at the Science Center Overbach in J\"ulich for four days and has about 25 participants coming from various parts of Germany.
The academy comprises lectures, a tour to the particle accelerator COSY and the high performance computing facility at the Research Center J\"ulich as well as one full day of practical work.
Given the setting the participating students are highly motivated and eager to understand.
